Implicit yaddayadda

### 2011-10-28 papers/PLDI2012/implicitization.tex
typo
uniformisation apparence du code

The expected inductive invariant is $\verb|x_old| \in [-100000,100000]$, but classical abstract interpretation using intervals (or octagons or polyhedra) finds $\verb|x_old| \in (-\infty,+\infty)$~\citep{ASTREE_ESOP05}.
Let us briefly see why.

@@

In cases where the formula is expressed in too rich a logic for the SMT-solver to deal with, a number of workarounds are possible:
\begin{itemize}[itemsep=-\parsep,topsep=0pt,partopsep=0pt]
\item \emph{Linearization}, as per \citet{DBLP:conf/vmcai/Mine06}, which overapproximates nonlinear semantics by linear semantics.
\item Replacing the results of nonlinear operations by ``unknown''.
\end{itemize}
However, such transformations are not yet implemented in our tool.
\DM{c'est si dur de remplacer * non lineaire par undef?}

>>>>

The expected inductive invariant is $\lstinline|x_old| \in [-100000,100000]$, but classical abstract interpretation using intervals (or octagons or polyhedra) finds $\lstinline|x_old| \in (-\infty,+\infty)$~\citep{ASTREE_ESOP05}.
Let us briefly see why.

@@

In cases where the formula is expressed in too rich a logic for the SMT-solver to deal with, a number of workarounds are possible:
\begin{itemize}[itemsep=-\parsep,topsep=0pt,partopsep=0pt]
\item \emph{Linearization}, as per \citet{DBLP:conf/vmcai/Mine06}, which overapproximates nonlinear semantics by linear semantics. However, such transformations are not implemented in our tool.
\item Replacing the results of nonlinear operations by ``unknown''.
\end{itemize}
